---
output: github_document
---

  [![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# add2deployment

The goal of add2deployment is to
R functions for translating R to SQL for deployment.

In the early phase of modeling, the user data is not large, thus the modelers choose to deploy the model they train on Mysql or Impala.

I do such sort of things a lot and think build some defined functions to reduce the translating time (from R code to SQL-like code).

## Installation

You can install the released version of add2deployment from [Github](https://github.com/JiaxiangBU/add2deployment) with:

```{r eval=F}
devtools::install_github('JiaxiangBU/add2deployment')
```

```{r eval=F}
library(add2deployment)
```

## Example

See the vignettes.
