---
title: "tranlate PCA model from R to SQL"
author: "Jiaxiang Li"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    fig_caption: yes
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```



There are three kind of variables

1. factor variable
1. continous variable
1. binary variable
: data type is `dbl` in `data.frame` but there are only two distinct value (like 1,0).



```{r}
library(tidyverse)
set.seed(123)
sample_data <- 
cbind(
    matrix(
        c(
            1:100
        )
        ,nrow = 10
        ,byrow = F
    )
    ,matrix(
        c(
            letters[1:20]
        )
        ,nrow = 10
        ,byrow = T
    )
    ,matrix(
        c(
            rep(0:1,5)
        )
        ,nrow = 10
        ,byrow = T
    )
) %>% 
    `colnames<-`(paste0('v',1:13)) %>% 
    `rownames<-`(1:10) %>% 
    as.data.frame() %>% 
    mutate_at(vars(1:10,13),as.integer) %>% 
    mutate_at(vars(1:10),~cut_number(.,3))
sample_data
library(caret)
sample_data_after_onehot <- 
    sample_data %>% 
    predict(dummyVars(~.,data=.),newdata =.) %>%
    as.data.frame()
sample_data_after_onehot
library(irlba)
pca_score <- prcomp_irlba(sample_data_after_onehot,n=2,center = T,scale. = F)
```

1. `sample_data` is discretized for all continuous variable by `cut_number`. 
1. Here I use `prcomp_irlba` instead of `prcomp` partly because `prcomp` is hard to train big data.
1. `dummyVars` function I use is to one-hot encoding the category variables.

```{r}
r_output <- 
    pca_score$rotation %>% 
    `rownames<-`(sample_data_after_onehot %>% names) %>% 
    as.data.frame() %>% 
    rownames_to_column('variable')
r_output
```

`r_output` is what I get when I finish the pca model.

Now, we recode it in SQL style.

```{r}
library(add2deployment)
trans_inSQL(input=r_output)
```
